---
title: "Final Output Machine Learning"
author: "Erik Schulte"
date: "30 6 2022"
bibliography: Tex/ref.bib
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction \label{Introduction}

References are to be made as follows: @fama1997[p. 33] and @grinold2000 Such authors could also be referenced in brackets [@grinold2000] and together [@fama1997 \& @grinold2000]. Source the reference code f

# Data  {-}
First of all, I present all relevant data sources and explain essential features to get a
proper overview. Afterwards, I explain the process of loading the data into R and how
we process the raw text corpus, to obtain meaningful results.

## Data Sources

For our empirical analysis we use three main data sources. The ﬁrst two data sources are
used for the text analysis and the building of the subgroups. Data on the speeches of
the UNSC were obtained from @schonfeld2019. It contains 82165 speeches over
the years 1995 until 2017.

```{r, echo=TRUE, warning=FALSE, message=FALSE}
#load required packages
library(tidyverse)
library(readtext)
library(quanteda)
library(quanteda.textplots)
library(quanteda.textstats)
library(ggplot2)
library(magrittr)
library(gdata)
library(kableExtra)


#load the UN Security Council Debates dataset
load("data/dataset.RData")
load("data/docs.RData")

#set a seed for reproducability
set.seed(2333)
# View data
#head(meta_meetings)
#head(meta_speeches)
```


