---
title: "China wulf warrior diplomacy"
subtitle: Practical
documentclass: elsarticle
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Entry1: Final Project Data Science.
Entry2: \textbf{Erik Valentin Schulte}
Entry3: A project submitted for the Data Science 2022 class
Uni_Logo: Tex/SU_horizontal.png
Logo_width: 0.8
Entry4: 'Under the supervision of: \vfill Dawie van Lill'
Entry5: Stellenbosch University
Entry6: April 2022
Entry7: null
Entry8: null
AddTitle: yes
Author1: Erik Valentin Schulte^[__Contributions:__  \newline _The authors would like
  to thank no institution for money donated to this project. Thank you sincerely._]
Ref1: Stellenbosch University, Stellenbosch, South Africa
Email1: 26802325\@sun.ac.za
CorrespAuthor_1: yes
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
Thesis_FP: yes
abstract: |
  Cool Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, echo=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
#load required packages
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(readtext)
library(quanteda)
library(quanteda.textplots)
library(quanteda.textstats)
library(ggplot2)
library(magrittr)
library(gdata)
library(kableExtra)


#load the UN Security Council Debates dataset
load("data/dataset.RData")
load("data/docs.RData")

#set a seed for reproducability
set.seed(2333)
# View data
#head(meta_meetings)
#head(meta_speeches)
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

References are to be made as follows: @fama1997[p. 33] and @grinold2000 Such authors could also be referenced in brackets [@grinold2000] and together [@fama1997 \& @grinold2000]. Source the reference code f


```{r}
corpus <- (meta_speeches)
Chinaspeeches <- subset.data.frame(corpus, country == "China") #only the speeches from China

```



```{r}
set.seed(1234)
word_pairs %>%
  filter(n >= 30) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "darkred") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()
```


```{r, include=FALSE, results='hide'}
speech_words_CHN_per_speech$speech <- as.integer(speech_words_CHN_per_speech$speech)
speech_words_CHN_per_speech <- as_tibble(speech_words_CHN_per_speech)

# we need to filter for at least relatively common words first
word_cors <- speech_words_CHN_per_speech %>%
  #as.character(speech_words_CHN_per_speech$speech) |> 
  #  as.factor(speech_words_CHN_per_speech$word) |> 
  group_by(word) %>%
  filter(n() >= 1000) %>%
  pairwise_cor(word, speech, sort = TRUE)

head(word_cors)

str(speech_words_CHN_per_speech)
#In particular, here we’ll focus on the phi coefficient, a common measure for binary correlation. The focus of the phi coefficient is how much more likely it is that either both word X and Y appear, or neither do, than that one appears without the other @tidytext. The phi coefficient is equivalent to the Pearson correlation. The pairwise_cor() function in widyr lets us find the phi coefficient between words based on how often they appear in the same speech.
```


This output format is helpful for exploration. Again this data frame, is extremly long somehow with more than 182 million rows and many word with a correlation of infinity and also negative values which does not make sense. For example, we could find the words most correlated with a word like “africa” using a filter operation.

```{r, include=FALSE, results='hide'}
word_cors %>%
  filter(item1 == "africa")
```

I then pick some particularly interesting words and check which words are most associated with them.
```{r, include=FALSE, results='hide'}
word_cors %>%
  filter(item1 %in% c("america", "europe", "africa")) %>%
  group_by(item1) %>%
  slice_max(correlation, n = 6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```

```{r, include=FALSE, results='hide'}
set.seed(2016)

word_cors %>%
  filter(correlation == 1) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void()
```

# Data  {-}
First of all, I present all relevant data sources and explain essential features to get a
proper overview. Afterwards, I explain the process of loading the data into R and how
we process the raw text corpus, to obtain meaningful results.


#  Methodology \label{Meth}

## Subsection
Ideally do not overuse subsections. It equates to bad writing.^[This is an example of a footnote by the way. Something that should also not be overused.]

## Math section



# Results


## Huxtable


\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

